### 2009-02-03 articles/2009/geoinformatics/article.tex
Added perspective/conclusion, hopefully not to heavy on the marketing...
git-svn-id: https://svn.osgeo.org/qgis/trunk@10097 c8812cc2-4d05-0410-92ff-de0c093fc19c

One of the curious aspects of being a Free and Open Source project is that we 
have very little idea of exactly how many users we have. Since the software can 
be freely copied and passed around after it is downloaded it is difficult to 
judge useage numbers. With around 1550 registered users on our community map 
we can extrapolate a user base in excess of 15000 given a conservative 
estimate of a 1% sign up rate.

@@

@@

Otto Dassau <dassau@nature-consult.de>: Otto lives in Hannover, Germany. His
background is Open Source GIS and applied remote sensing. 
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>

>>>>

One of the curious aspects of being a Free and Open Source project is that we 
have very little idea of exactly how many users we have. Since the software can 
be freely copied and passed around after it is downloaded it is difficult to 
judge useage numbers. With around 1550 registered users on our community map 
we can extrapolate a user base in excess of 15000 given a conservative 
estimate of a 1\% sign up rate.

@@

Quantum GIS began as a one-developer application that was met with skepticism
by many asking ``Why another open source GIS?''. Although the initial goals
were modest, QGIS has become a mature and extensible tool for viewing,
editing, and performing GIS analysis. Creating a feature-complete GIS from
scratch is a tremendous undertaking and at the outset was not really a goal of
the project. With the GRASS integration and the extensibility possible through
plugins, QGIS is positioned to grow into an even more robust toolset for the
GIS user.

Early in life, the QGIS community was small and grew quite slowly.
With the addition of several key developers, the features and capabilities
expanded rapidly and with it, the community. QGIS now has an established
community providing peer support, testing, and new features via plugins.

At version 1.0, QGIS provides a rich, stable API from which developers can
create custom solutions in Python or C++. As the project moves forward, 
there are many exciting developments underway in both the core application and
plugins.

While it took nearly 7 years to get to version 1.0, the process is a
testimony to the power of open source in bringing the talents and ideas of
many individuals together to create a tool used by thousands in academia,
government, and private industry around the world.

@@

Otto Dassau <dassau@nature-consult.de>: Otto lives in Hannover, Germany. His
background is Open Source GIS and applied remote sensing. 
\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been torturing computers and programming languages well over two decades. In 2002 he founded the Quantum GIS project. 
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>
